\section{Linear Maps and Matrices}
The set of linear maps from $V$ to $W$ is a vector space over the same field $F$.
\begin{definition}
    Let $V,W$ be vector spaces over $F$.
    We define
    $$L(V,W)=\{\alpha:V\to W\text{, linear}\}$$
    to be the vector space of linear maps from $V$ to $W$ under the operations $(\alpha+\beta)(v)=\alpha(v)+\beta(v)$ and $(\lambda\alpha)(v)=\lambda\alpha(v)$.
\end{definition}
It is easy to verify that this is indeed a vector space.
There is a very important theorem
\begin{proposition}\label{linear_map_matrices}
    If $V,W$ are finite dimensional, so is $L(V,W)$ and we have $\dim L(V,W)=(\dim V)(\dim W)$.
\end{proposition}
\begin{definition}
    An $m\times n$ matrix over $F$ is an array with $m$ rows and $n$ columns with entries in $F$.
    As a convention, for a matrix $A$ we write $A=(a_{ij})_{1\le i\le m,1\le j\le n}=(A_{ij})_{1\le i\le m,1\le j\le n}$ where $i$ refers to the row number and $j$ the column number.
    We write $M_{m,n}(F)$ to denote the set of $m\times n$ matrices over $F$.
\end{definition}
Note that we can (and often) identify vectors in $\mathbb R^m$ as $m\times 1$ matrices.
\begin{proposition}
    $M_{m,n}(F)$ is a vector space over $F$ under $(a_{ij})+(b_{ij})=(a_{ij}+b_{ij})$ and $\lambda(a_{ij})=(\lambda a_{ij})$.
\end{proposition}
\begin{proof}
    Trivial.
\end{proof}
\begin{proposition}
    $\dim M_{m,n}(F)=mn$.
\end{proposition}
\begin{proof}
    The set $\{(\delta_{ia}\delta_{jb}):1\le a\le m,1\le b\le n\}$ with size $mn$ is a basis of $M_{m,n}(F)$.
\end{proof}
We want to represent linear maps by matrices.
For $V,W$ vector spaces over $F$ of finite dimensions $n,m$, we choose ordered bases $B=(v_1,\ldots,v_n),C=(w_1,\ldots,w_m)$ for $V,W$ respectively.
For $v\in V$, its coordinate under $B$ is $[v]_B=(v_1,\ldots,v_n)$ where $v=\sum_{i}v_ib_i$ is the unique decomposition of $v$ in this basis.
Similarly, the coordinate of $w\in W$ under $C$ is $[w]_C=(w_1,\ldots,w_m)$ where $w=\sum_{i}w_ic_i$ is the unique decomposition of $w$ under $C$.
\begin{definition}
    The matrix of $\alpha:V\to W$ in the bases $B,C$ is the matrix
    $$([\alpha]_{B,C})_{ij}=(\alpha(v_j))_i\in M_{m\times n}(F)$$
\end{definition}
If the bases are understood, we often write $([\alpha]_{B,C})_{ij}$ as $\alpha_{ij}$.
\begin{definition}
    For matrices $M\in M_{m\times n}(F)$ and $N\in M_{n\times l}(F)$, their matrix product is the $m\times l$ matrix defined by $(MN)_{ij}=(\sum_kM_{ik}N_{kj})_{ij}$.
\end{definition}
The particular case where $N$ is a column vector exhibits how $m\times n$ matrices induce linear maps $F^n\to F^m$.
\begin{lemma}
    For any $v\in V$,
    $$[\alpha(v)]_C=[\alpha]_{B,C}[v]_B$$
\end{lemma}
\begin{proof}
    Linearity.
\end{proof}
We already know that composition of linear maps is linear, what's more is
\begin{lemma}
    Let $U,V,W$ be finite dimensional vector spaces over $F$ with chosen bases $A,B,C$ respectively.
    Let $\beta:U\to V$ and $\alpha:V\to W$ be linear maps, then
    $$[\alpha\circ\beta]_{A,C}=[\alpha]_{B,C}[\beta]_{A,B}$$
\end{lemma}
\begin{proof}
    Linearity again.
\end{proof}
\begin{proposition}
    We have $L(V,W)\cong M_{m\times n}(F)$ via $\alpha\mapsto[\alpha]_{B,C}$ where $B$ is a basis of $V$ and $C$ is a basis of $W$.
\end{proposition}
\begin{proof}
    Just check.
\end{proof}
\begin{proof}[Proof of Proposition \ref{linear_map_matrices}]
    Simple corollary of the preceding proposition.
\end{proof}
\begin{remark}
    Let $\alpha:V\to W$ be linear.
    The diagram
    \[
        \begin{tikzcd}
            V\arrow{r}{\alpha}\arrow[swap]{d}{v\mapsto [v]_B}&W\arrow{d}{w\mapsto [w]_C}\\
            F^n\arrow[swap]{r}{[\alpha]_{B,C}}&F^m
        \end{tikzcd}
    \]
    commutes.
\end{remark}
\begin{example}
    Let $\alpha:V\to W$ be linear and $Y\le V$ a subspace.
    Let $B$ be a basis of $V$ extending a basis $B'$ of $Y$ and $C$ a basis of $W$ extending a basis $C'$ of $Z\ge\alpha(Y)$.
    Then the entries of $[\alpha]_{B,C}$ that are relevant to $B'\subset B,C'\subset C$ are exactly $[\alpha|_{Y\to Z}]_{B',C'}$.
    So if we rearrange the bases so that $B'$ are in the front of $B$ and $C'$ in the front of $C$, then the matrix will look like
    $$[\alpha]_{B,C}=\left(\begin{array}{c|c}
        [\alpha|_{Y\to Z}]_{B',C'}&\ast\\
        \hline
        0&\ast
    \end{array}\right)$$
\end{example}
\begin{proposition}
    Let $\alpha:V\to W$ be linear and $\alpha(Y)\le Z\le W$, then $\alpha$ induces a map $\bar\alpha:V/Y\to W/Z$ via $v+Y\mapsto\alpha(v)+Z$.
\end{proposition}
\begin{proof}
    Trivial.
\end{proof}